Prefetching SPARQL query cacher

### 2016-05-16 dissertation/cache-proxy.tex
about planning and stores

@@

>>>>

For this work, the usage of roles to simplify query planning is of
particular importance. While we do not exploit optimisations closer to
the database, we extend the query planner in several directions with
several separate add-on modules, with only generic functionality in
the core Attean framework.

We have found it convenient to use classical inheritance in
combination with traits-based composition, but only when the base
class provide only fundamental functionality that is very likely to be
common to all implementations. For an example of this, see
Section~\ref{sec:cacher}.

Also of importance are the APIs to compose stores. Stores in Attean
can be triplestores or quadstores, they can be mutable,
bulkupdateable, can enable the use of \httph{ETag}s or modification
times for conditional requests, and makes possible further
extensions. Each of these primitives is represented by a role that
implements default functionality or simply requires such functionality
to be required. For instance, a quadstore is required by
\pmodule{Attean::API::QuadStore} to implement the \pcode{get\_quads}
method, which can take an RDF term as one or more of the arguments and
variables for the rest, and should return an iterator over the quads
that were matched. Based on an implementation of the
\pcode{get\_quads} method, the \pmodule{Attean::API::QuadStore} role
provides default implementations of methods \pcode{count\_quads},
\pcode{count\_quads\_estimate}, \pcode{get\_graphs} and
\pcode{size}. These methods may be overridden when composing a
class. Composing other roles will require further methods to be
implemented.\todo{Explain Model}

@@

\subsection{The query proxy}\label{sec:cacher}

For example, the query planner that can use a local cache and a remote
endpoint, named \pmodule{AtteanX::QueryPlanner::Cache}, extends the
basic query planner of the Attean framework,
\pmodule{Attean::QueryPlanner}, but also composes the following roles:
\pmodule{Attean::API::NaiveJoinPlanner},
\pmodule{Attean::API::SimpleCostPlanner},
\pmodule{AtteanX::API::JoinRotatingPlanner},
\pmodule{AtteanX::Query::AccessPlan::SingleQuadBGP} and
\pmodule{AtteanX::Query::AccessPlan::Cache}.
